\thesistitle

### 2019-11-22 pldi/paper.tex
Terminology and techniques

\section{Background}
We describe code clone definitions and techniques that are commonly used in code clone detection.

\subsection{Clone type definitions}
Most modern clone detection tools detect clones by the following clone type definitions \cite{svajlenko2014evaluating}:
\textbf{Type 1:} Code fragments that are syntactically identical, except for differences in white space, layout and comments.
\textbf{Type 2:} Code fragments that are syntactically identical, except for differences in identifier names, literal values, white space, layout and comments.
\textbf{Type 3:} Code fragments that are syntactically similar with differences at the statement level. The fragments may differ by the addition, removal or modification of statements.

\subsection{Clone detection techniques}

\section{Clone Detection Techniques Survey}
As an initial step towards creating a clone detection DSL, we surveyed clone detection techniques and tools to extract common functionalities.

@@

Based on such thresholds, clones that are too small are filtered. How these thresholds are configured has a big impact on the results and their relevance \cite{roy2007survey}. Our DSL allows for any combination of metric values to configure the minimum size of a clone. For this, we introduce the \textbf{Size} keyword. This is an example of how the \textbf{Size} keyword can be configured:
\\
\textbf{\textcolor[HTML]{7F0055}{Size}} (\textcolor[HTML]{7D7D7D}{4} \textbf{\textcolor[HTML]{7F0055}{lines}} $\&$  \textcolor[HTML]{7D7D7D}{50} \textbf{\textcolor[HTML]{7F0055}{tokens}}) $ \vert $  (\textcolor[HTML]{7D7D7D}{6} \textbf{\textcolor[HTML]{7F0055}{lines}} $\&$  \textcolor[HTML]{7D7D7D}{40} \textbf{\textcolor[HTML]{7F0055}{tokens}})
\\

>>>>

\section{Background}
We describe terminology, definitions and techniques that are commonly used in code clone detection.

\subsection{Code clone terminology}
To argue about code clones, we use the following terminology:
\\ \textbf{Code fragment} \cite{svajlenko2019mutation}: A continuous region of source code. Specified by the triple $(l,s,e)$, including the source file \textit{l}, the start line and column \textit{s}, and the end line and column \textit{e}.
\\ \textbf{Clone class} \cite{roy2007survey}: A set of similar code fragments. The definition of similarity depends on the desired granularity of clones.
\\ \textbf{Clone instance} \cite{roy2007survey}: A cloned code fragment that is part of a clone class.

\subsection{Clone type definitions}
Most modern clone detection tools detect clones by the following clone type definitions \cite{svajlenko2014evaluating}:
\\ \textbf{Type 1}: Code fragments that are syntactically identical, except for differences in white space, layout and comments.
\\ \textbf{Type 2}: Code fragments that are syntactically identical, except for differences in identifier names, literal values, white space, layout and comments.
\\ \textbf{Type 3}: Code fragments that are syntactically similar with differences at the statement level. The fragments may differ by the addition, removal or modification of statements.

\subsection{Clone detection techniques}
Different clone detection techniques have been proposed in literature \cite{sheneamer2016survey}:
\textbf{Textual}: Code lines are textually compared. Advantages are that textual approaches are often simpler, easier to implement and are independent of language. Disadvantages are that it is harder to exclude certain constructs from matching.
\\ \textbf{Lexical (Token)}: Lexical approaches first tokenize the source code, so certain groups of tokens can be excluded from matching \cite{svajlenko2014evaluating}. The disadvantage is that tokens must be specified for each language.
\\ \textbf{Syntactic (Tree)}: AST-based approaches first parse the source code into an AST. This allows for subtree based comparison and mapping context of clones \cite{fontana2015duplicated}.
\\ \textbf{Syntactic (Metric)}: In metric-based clone detection techniques, a number of metrics are computed for each fragment of code to find similar fragments by comparing metric vectors instead of comparing code or ASTs directly.
\\ \textbf{Semantic (Graph)}: A graph-based clone detection technique uses a graph to represent the data and control flow of a program.
\\ \textbf{Semantic (Hybrid)}: Hybrid approaches use a combination of before-mentioned techniques to speed up detection of clones and find clones with a variety of characteristics.

\section{Clone Detection Techniques Survey}
As an initial step towards creating a clone detection DSL, we survey clone detection techniques and tools to extract common functionalities. \todo{Write this section}

@@

Based on such thresholds, clones that are too small are filtered. How these thresholds are configured has a big impact on the results and their relevance \cite{roy2007survey}. Our DSL allows for any combination of metric values to configure the minimum size of a clone. For this, we introduce the \textbf{Size} keyword. This is an example of how the \textbf{Size} keyword can be configured:

\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\textbf{\textcolor[HTML]{7F0055}{Size}} (\textcolor[HTML]{7D7D7D}{4} \textbf{\textcolor[HTML]{7F0055}{lines}} $\&$  \textcolor[HTML]{7D7D7D}{50} \textbf{\textcolor[HTML]{7F0055}{tokens}}) $ \vert $  (\textcolor[HTML]{7D7D7D}{6} \textbf{\textcolor[HTML]{7F0055}{lines}} $\&$  \textcolor[HTML]{7D7D7D}{40} \textbf{\textcolor[HTML]{7F0055}{tokens}})\\
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

In this example, we seek clones that either have many tokens but fewer lines, or many lines but fewer tokens. We allow the following keywords to be used in the condition of the \textbf{Size} threshold:
\begin{itemize}
  \item \textit{lines}: Number of lines found in each clone instance
\end{itemize}
